---
title       : Project Documentation 
subtitle    : How to predict car fuel efficiency online
author      : Lingli Peng
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Online Prediction Application

- This application provides a convenient way for people to check the car fuel efficiency online
- It applies prediction based on regression modeling 
- It is coded using rstudio and shiny 

---

## How to Use the Online Application

1. Go to https://linglipeng.shinyapps.io/DataProductProject
2. Input values for both car weight (lb/1000) and number of cylinders
3. The application allows minimum of 1 and maxmum of 6 when inputing car weight
4. The provided input choices for number of cylinders are 4, 6 and 8
5. The predicted car miles per gallon value will be automatically calculated and displayed based on the input values

---

## Dataset mtcars

- mtcars dataset is used to build a regression model for the prediction. It comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles

```{r}
data(mtcars)
str(mtcars)
```

---

## Prediction Example

- Here is an example of prediction based on regression modeling with the mtcars dataset
- Predictors are weight (wt) and number of cylinders (cyl)
- Response is mileage per gallon (mpg)

```{r}
data(mtcars)
x1 <- mtcars$wt
x2 <- mtcars$cyl
y <- mtcars$mpg
lm1 <- lm(y ~ x1 + factor(x2))
predict(lm1, newdata=data.frame(x1=3,x2=6))[[1]]
```

- The predicted mpg value is 20.12 for a car of 3000 lb and 6 cylinders
